Video Understanding : A review of action detection-recognition dataset*\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-01-11 conference_101719.tex
origin

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[utf8]{vietnam}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{Introduction}
In the past decade, deep learning models have achieved remarkable success and have outperformed traditional methods in various tasks, including object detection, sound source separation, action recognition, and more. Currently, there is an increasing number of research studies being conducted to apply and improve existing models or create new architectures to address real-world problems. The rapid success of deep learning models can largely be attributed to two factors: the advancement of computer hardware in terms of computational power and memory capacity, as well as the expanding scale of available datasets.

\textbf{Advancement of computer hardware} :

\begin{center}
	\includegraphics[width=1.0\linewidth]{fig_info/fig1/Figure_1}
	\caption{Example of a figure caption.}
	\label{SSD300} 
\end{center}
